### 2019-01-03 taco/tex/evaluation.tex
revise some errors

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
Although the effect of \textit{pre-scheduling} will be alleviated by the simple DAG computing, some shuffle-heavy jobs can still be optimized by SCache shuffle data management.

% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and the reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

>>>>

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.

% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and the reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce phase needs to wait for network transfer. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

### 2019-01-03 taco/tex/intro.tex
revise some errors

{\color{blue}
In order to analyze above-mentioned resources scheduling strategies, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}

>>>>

{\color{blue}
To analyze resources scheduling strategies as mentioned above, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}

### 2019-01-03 taco/tex/model.tex
revise some errors

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
The FRQ model quantifies computing and I/O resources and visualizes them in time dimension. According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on. Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed computing frameworks mostly use DAGs to describe computation logic. 
A shuffle phase is required between each adjacent DAG computation phases. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
\begin{itemize}
	\item Input Data Size \((D)\): The data size of the computation phase.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. This rounds depends on the current computation resources and the configuration of the framework. Taking Hadoop MapReduce as an example, supposing we have 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map require 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
    The computation speed for each computation phase. This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
    Transmission speed during shuffle. This speed depends on network and storage device bandwidth.
\end{itemize}

@@

\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of shuffle phase. 
The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results. The overhead is caused by these waiting. The FRQ model uses K to indicate the extent of the waiting.

@@

The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a simple scheduling strategy which used by Apache Spark by default. 
As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is fully serially executed. The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the reduce phase is 0. The total execution time of a job is also different from the above:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}

Due to serialization, the I/O resource is idle during the reduce phase and map phase. this scheduling strategy is simple and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows a more efficient scheduling strategy which is used by Hadoop MapReduce. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to Equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see Equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. 
But we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.

@@

\subsection{Model Verification}\label{model_verification}
In order to verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}. (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node. To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop Mapreduce framework. We deployed Hadoop with SCache and without SCache in both environments.

@@

In order to verify the above-mentioned two cases when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed. On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment. 
Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
% Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.

In terms of accuracy, the experimental values are all larger than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on. 
% In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
These overhead will be amplified when the input data is small or the total execution time is short. 
Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
}

>>>>

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on. Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed computing frameworks mostly use DAGs to describe computation logic. 
A shuffle phase is required between each adjacent DAG computation phases. To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model can describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
\begin{itemize}
	\item Input Data Size \((D)\): The data size of the computation phase.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. These rounds depend on the current computation resources and the configuration of the framework. Take Hadoop MapReduce as an example. Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
    The computation speed for each computation phase. This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
    Transmission speed in the shuffle phase. This speed depends on network and storage device bandwidth.
\end{itemize}

@@

\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results. This waiting causes the overhead. The FRQ model uses K to indicate the extent of the waiting.

@@

The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a simple scheduling strategy which used by Apache Spark by default. 
As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is entirely serially executed. The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the reduce phase is 0. The total execution time of a job is also different from the above:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}

Due to serialization, the I/O resource is idle during the reduce phase and map phase. This scheduling strategy is simple and has much room for optimization.

Figure \ref{fig:model_hadoop} shows a more efficient scheduling strategy which is used by Hadoop MapReduce. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to Equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see Equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. 
However, we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.

@@

\subsection{Model Verification}\label{model_verification}
To verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}. (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node. To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop Mapreduce framework. We deployed Hadoop with SCache and without SCache in both environments.

@@

In order to verify the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed. On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment. 
Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
% Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.

Regarding accuracy, the experimental values are all larger than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on. 
% In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
This overhead will be amplified when the input data is small or the total execution time is short. 
Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
}
